Computing Exact Restricted Isometry Constants via\\ Mixed Integer Semidefinite Programming

### 2016-03-14 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
correction in the explanation of Asp08, Psi should be the optimal objective, not solution

As shown in \cite{Asp08}, a lower bound for $\alpha_k$ can be computed via
\begin{equation*}
 \alpha_k^2 \geq \sup_{\rho \geq 0}\; \psi(\rho) - \rho\, k,
\end{equation*}
with 
\begin{equation*}
  \psi(\rho) = \min \big\{ x\T \Sigma\, x + \rho \Norm{x}{0} \suchthat \Norm{x}{2} \leq 1\big\}.
\end{equation*}
\comment{$\bar{X}$ L\"osung von \eqref{Asp08}?}
In this case problem \eqref{Asp08} or equivalently \eqref{Asp08Dual} has to
be solved for $\Sigma = M I - A\T A$, where $M \in \R$ has to be big enough
to make $\Sigma$ positive semidefinite again. If $\bar{X}$ is a
corresponding optimal solution, this implies a lower bound on $\alpha_k$
in\comment{Ist $M\,I$ statt $M$ korrekt?}
\begin{equation*}
  \alpha_k^2 \geq \sup_{\rho \geq 0}\; (M\, I - \bar{X}) - \rho\, k.
\end{equation*}
In \cite{AspBG14} explicit bounds on the quality of this relaxation where derived using randomization arguments.
\comment{Ist hier die Lagrange-Relaxierung gemeint?}

>>>>

As shown in \cite{Asp08}, a lower bound for $\alpha_k$ can be computed via
\begin{equation*}
 \alpha_k^2 \geq \sup_{\rho \geq 0}\; \psi(\rho) - \rho\, k,
\end{equation*}
with 
\begin{equation*}
  \psi(\rho) = \min \big\{ x\T \Sigma\, x + \rho \Norm{x}{0} \suchthat \Norm{x}{2} \leq 1\big\}.
\end{equation*}
In this case problem \eqref{Asp08} or equivalently \eqref{Asp08Dual} has to
be solved for $\Sigma = M I - A\T A$, where $M \in \R$ has to be big enough
to make $\Sigma$ positive semidefinite again. If $\Psi$ is the
corresponding optimal objective, this implies a lower bound on $\alpha_k$
in\comment{Ist $M\,I$ statt $M$ korrekt? \\ $\Rightarrow$ nein, sollten alles Skalare sein, $\Psi$ demenstrechend optimaler Zielfunktionswert statt L\"osung (habe ich jetzt oben angepasst)}
\begin{equation*}
  \alpha_k^2 \geq \sup_{\rho \geq 0}\; (M - \Psi) - \rho\, k.
\end{equation*}
In \cite{AspBG14} explicit bounds on the quality of this relaxation where derived using randomization arguments.
\comment{Ist hier die Lagrange-Relaxierung gemeint?}
